Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-07-27 Final_Manuscript.Rmd
fixed reference

author: 
  - name          : "Randi L. Garcia"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "415 Bass Hall, Smith College, Northampton, MA 01060"
    email         : "rgarcia@smith.edu"
  - name          : "Kat Kyuchukova"
    affiliation   : "1"
  - name          : "Asha Hinson"
    affiliation   : "1"
  - name          : "Lanee Jung(edit)"
    affiliation   : "1"

@@

##Interpersonal Objectification
SIMO model and literature review [@gervais2020social]. Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979]. Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredricksonetal1998]. We don't know about women-on-women interpersonal objectification. What might be different?

@@

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
```
Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredricksonetal1998; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus non-observable ways. The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts. Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness). Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.

>>>>

author: 
  - name          : "Randi L. Garcia"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "415 Bass Hall, Smith College, Northampton, MA 01060"
    email         : "rgarcia@smith.edu"
  - name          : "Kat Kyuchukova"
    affiliation   : "1"
  - name          : "Asha Hinson"
    affiliation   : "1"
  - name          : "Lanee Jung"
    affiliation   : "1"

@@

##Interpersonal Objectification
SIMO model and literature review [@gervais2020social]. Studies have shown that within social encounters women are gazed at more than men [@briton1995], often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on physical self [@puvia2013being; @young1979]. Moreover, perhaps the most adverse effect of objectifying treatment is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated, an effect termed self-objectification  [@Bartky; @berger1972; @fredrickson1998swimsuit]. We don't know about women-on-women interpersonal objectification. What might be different?

@@

#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith_final, tso_1, tso_2, tso_4, tso_7, tso_9), check.keys=TRUE)$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith_final, tso_3, tso_5, tso_6, tso_8, tso_10), check.keys=TRUE)$total[2]
```
Trait self-objectification (TSO) was assessed using the Self-Objectification Questionnaire [@fredrickson1998swimsuit; @nollfredrickson1998], which evaluates the extent to which individuals view their bodies in observable versus non-observable ways. The questionnaire asked participants to rank order both appearance and functional aspects of their bodies, from 1 (least important) to 10 (most important), with respect to physical self-concepts. Of the ten body attributes, five of the items were appearance-based (weight, sex appeal, physical attractiveness, firm/sculpted muscles and body measurements), and five of the items were competence-based (strength, physical coordination, energy level, health and physical fitness). Difference scores were computed by subtracting the sum of the 5 functional aspects/competence attributes (e.g., health, strength) from the sum of the 5 physical self-concepts/appearance attributes (e.g., physical attractiveness, weight), and all measures were multiplied by -1, as was done in @garcia2016objectification, so that positive scores indicated greater TSO.
